---
title: "Example"
author: "Catherine Gitau"
date: "August 20, 2019"
output: 
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE,message=FALSE,error=FALSE)
```

## Team Bla Bla Bla
### Team Members:
- Catherine GItau
- Person 2
- Person 3

# Bank Telemarketing Data Exploration

```{r}
#load in the libraries
library(tidyverse)
library(DT)
```

```{r cars}
# Load in the dataset
data <- read_csv("data/bank-additional.csv")
head(data)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

# Steps of Data Exploration and Preparation
1. Identify the type of variables in the data .. if it's the **Predictor(Input)** or the **Target(output) variable**
2. Identify the data type (either a character or numeric) and category(if it's Categorical or Continuous)
3. Calculate a set of summary statistics and explain what you find out about the data
4. Explore the variables and explain your findings using plots and explain why you chose to use that specific type of plot
5. Check if there are missing values and treat them accordingly
6. Identify Outliers
7. Find out which variables are highly correlated using a cor plot
7. Try and find out if there are more data points we can get from existing data (Feature Engineering)
